|

### 2022-11-30 appendix/appendix.Rmd
Changes appendix to comply with AJPS editorial policies

\appendix
\addtocounter{section}{1}

@@

## A Model of Legislature Size and Service Provision (Proofs)

@@

## Variable Sources and Descriptive Statistics
\label{appsources}

@@

### Outcomes Aggregated at the Municipal Level

@@

### Legislation Dataset

@@

### Online 2016 Former City Councilors Survey

@@

## Threshold Manipulation, Sorting, and Pre-Treatment Consistency

@@

## Population Thresholds in Brazil Before and After the 2003 Supreme Court Decision
\label{appidentif}

@@

## Identification Strategy in Regression Discontinuity Designs with Multiple Thresholds
\label{ISMT}

@@

## Placebo Regressions for the Political Mechanism
\label{placmechmain}

@@

## Sensitivity Analysis of Bandwidth Selection
\label{sensffapp}

@@

## Sensitivity Analysis of State Characteristics
\label{sensstate}

@@

## Sensitivity Analysis of Model Functional Form
\label{sensfuncform}

@@

## Sensitivity Analysis of Covariates
\label{senstcovapp}

@@

## Sensitivity Analysis of Additional Cutoffs

@@

## Mayors' Characteristics, Revenues, and Transfers from the Central Government

@@

### Mayors' Characteristics

@@

### Revenues and Transfers

@@

@@

## City Councilors Survey
\label{appsurv}

>>>>

\appendix

@@

# A Model of Legislature Size and Service Provision (Proofs)

@@

# Variable Sources and Descriptive Statistics
\label{appsources}

@@

## Outcomes Aggregated at the Municipal Level

@@

@@

## Online 2016 Former City Councilors Survey

@@

# Threshold Manipulation, Sorting, and Pre-Treatment Consistency

@@

# Population Thresholds in Brazil Before and After the 2003 Supreme Court Decision
\label{appidentif}

@@

# Identification Strategy in Regression Discontinuity Designs with Multiple Thresholds
\label{ISMT}

@@

# Placebo Regressions for the Political Mechanism
\label{placmechmain}

@@

# Sensitivity Analysis of Bandwidth Selection
\label{sensffapp}

@@

# Sensitivity Analysis of State Characteristics
\label{sensstate}

@@

# Sensitivity Analysis of Model Functional Form
\label{sensfuncform}

@@

# Sensitivity Analysis of Covariates
\label{senstcovapp}

@@

# Sensitivity Analysis of Additional Cutoffs

@@

# Mayors' Characteristics, Revenues, and Transfers from the Central Government

@@

## Mayors' Characteristics

@@

## Revenues and Transfers

@@

# Legislation Dataset

@@

# City Councilors Survey
\label{appsurv}
